---
title: "R Notebook"
output: html_notebook
---


---------------------------------------------------------------------------
2.1 Equality

```{r}
TRUE == TRUE 
```

```{r}
15 == (7+8)
```

```{r}
257 == (25*13)
```





---------------------------------------------------------------------------
2.1.1 Greater and less than



```{r}
12 * 45 + 10 > 5 + 4
```

```{r}
"ingenieria de software" < "software engineering"
```



2.1.2 Compare vectors

```{r}
# The linkedin and facebook vectors have already been created for you
linkedin <- c(16, 9, 13, 5, 2, 17, 14)
facebook <- c(17, 7, 5, 16, 8, 13, 14)

# Popular days
linkedin > 15
```

```{r}
Tienda1 <- c(150, 240 , 320, 180, 290)
Tienda2 <- c(135, 340, 280, 325, 170)

Tienda1 > 250

Tienda2 < 200

Tienda1 > Tienda2
```



2.1.3 Compare matrices

```{r}
# The social data has been created for you
linkedin <- c(16, 9, 13, 5, 2, 17, 14)
facebook <- c(17, 7, 5, 16, 8, 13, 14)

views <- matrix(c(linkedin, facebook), nrow = 2, byrow = TRUE)
views
```

```{r}
Ganancias <- matrix(c(Tienda1, Tienda2), nrow = 2, byrow = TRUE)
Ganancias
```

```{r}
Ganancias > 200
```

```{r}
Ganancias == 150
```



2.2 Logical Operators

2.2.1 & and |

```{r}
TRUE & TRUE
FALSE | TRUE
5 <= 5 & 2 < 3
3 < 4 | 7 < 6
```

```{r}
?tail
```

```{r}
# The linkedin and last variable are already defined for you
linkedin <- c(16, 9, 13, 5, 2, 17, 14)
last <- tail(linkedin, 1)

# Is last under 5 or above 10?
5 > last | last > 10
```

```{r}
UltimaGan <- tail(Tienda1, 1)

250 < UltimaGan | 289 < UltimaGan
```

```{r}
# Is last between 15 (exclusive) and 20 (inclusive)?
15 < last & last <= 20 
```

```{r}
289 < UltimaGan & UltimaGan <= 290
```


2.2.2 & and | (2)

```{r}
# linkedin exceeds 10 but facebook below 10
linkedin > 10 & facebook < 10
```

```{r}
Tienda2 > 330 & Tienda1 < 290
```


```{r}
# When were one or both visited at least 12 times?
linkedin >= 12 | facebook >= 12
```

```{r}
Tienda1 > 250 | Tienda2 > 250
```


```{r}
# When is views between 11 (exclusive) and 14 (inclusive)?
views > 11 & views <= 14
```

```{r}
Ganancias > 200 & Ganancias < 300
```



2.2.3 Blend it all together

```{r}
# Reading data
#li_df <- read.table(stdin(), header=TRUE) 
#li_df

#Writing data
# Write CSV in R
#write.csv(li_df, file = "data/li_df.csv")

## # li_df is pre-loaded in your workspace
#Loading data
li_df <- read.csv("data/li_df.csv")
#View(li_df)

# Select the second column, named day2, from li_df: second
second <- li_df$day2
second
```



2.3 Conditional Statements

2.3.1 The if statement

```{r}
# Variables related to your last day of recordings
medium <- "LinkedIn"
num_views <- 14

# Examine the if statement for medium
if (medium == "LinkedIn") {
  print("Showing LinkedIn information")
}
```

```{r}
Info1 <- "Abarrotes"
Ganan1 <- 250

if (Info1 == "Abarrotes") {
  print("Abarrotes doña Marta")
}
```

```{r}
# Write the if statement for num_views
if (num_views > 15) {
  print("You're popular!")
}
```

```{r}
if (Ganan1 > 200) {
  print("Las ganancias del dia fueron buenas")
}
```



2.3.2 Add an else

```{r}
# Variables related to your last day of recordings
medium <- "LinkedIn"
num_views <- 14

# Control structure for medium
if (medium == "LinkedIn") {
  print("Showing LinkedIn information")
} else {
  print("Unknown medium")
}
```

```{r}
Info1 <- "Abarrotes"
Ganan1 <- 190

if (Info1 == "Abarrotes") {
  print("Abarrotes doña Marta")
} else {
  print("No son los abarrotes doña Marta")
}
```


```{r}
# Control structure for num_views
if (num_views > 15) {
  print("You're popular!")
} else {
  print("Try to be more visible!")
}
```

```{r}
if (Ganan1 > 200) {
  print("Las ganancias del dia fueron buenas")
} else {
  print("No hubo buenas ganancias en el dia")
}
```



2.3.3 Customize further: else if

```{r}
# Variables related to your last day of recordings
medium <- "LinkedIn"
num_views <- 14

# Control structure for medium
if (medium == "LinkedIn") {
  print("Showing LinkedIn information")
} else if (medium == "Facebook") {
  # Add code to print correct string when condition is TRUE
  print("Showing Facebook information")
} else {
  print("Unknown medium")
}
```

```{r}
Info1 <- "Tiendita"
Ganan1 <- 290

if (Info1 == "Abarrotes") {
  print("Abarrotes doña Marta")
} else if (Info1 == "Tiendita"){
  print("Tiendita de la esquina")
} else {
  print("Tienda desconocida")
}
```


```{r}
# Control structure for num_views
if (num_views > 15) {
  print("You're popular!")
} else if (num_views <= 15 & num_views > 10) {
  # Add code to print correct string when condition is TRUE
  print("Your number of views is average")
} else {
  print("Try to be more visible!")
}
```

```{r}
if (Ganan1 > 300) {
  print("Fue un dia de excelentes ganancias")
} else if (Ganan1 > 200 & Ganan1 <= 300) {
  print("Las ganancias fueron buenas")
} else {
  print("No hubo buenas ganancias el dia de hoy")
}
```



2.3.4 Else if 2.0

```{r}
number <- 5

if (number < 10) {
  if (number < 5) {
    result <- "extra small"
  } else {
    result <- "small"
  }
} else if (number < 100) {
  result <- "medium"
} else {
  result <- "large"
}
print(result)
```

```{r}
Numeros <- 150000

if (Numeros >= 1000 & Numeros < 999999) {
  if (Numeros >= 100 & Numeros < 999) {
    result <- "Cienes"
  } else {
    result <- "Miles"
  }
} else if (Numeros >= 1000000){
  result <- "Millones"
} else {
  result <- "Mayor a los millones"
}

result
```








3 Loops

3.0.1 Write a while loop

```{r}
speed <- 64

# Code the while loop
while (speed > 30) {
  print("Slow down!")
  speed <- speed - 7
}
```

```{r}
Temperatura <- 90

while (Temperatura > 70) {
  print("Temperatura muy alta")
  Temperatura <- Temperatura - 6
}
```




3.0.2 Throw in more conditionals

```{r}
# Initialize the speed variable
speed <- 64

# Extend/adapt the while loop
while (speed > 30) {
  print(paste("Your speed is", speed))
  if (speed > 48) {
    print("Slow down big time!")
    speed <- speed - 11
  } else {
    print("Slow down!")
    speed <- speed - 6
  }
}
```

```{r}

Temperatura <- 90


while (Temperatura > 40) {
  print(paste("La temperatura es de", Temperatura))
  if (Temperatura > 70) {
    print("Temperatura muy alta")
    Temperatura <- Temperatura - 11
  } else {
    print("Bajando temperatura")
    Temperatura <- Temperatura - 6
  }
}
```




3.0.3 Stop the while loop: break

```{r}
# Initialize the speed variable
speed <- 120

while (speed > 30) {
  print(paste("Your speed is", speed))
  
  # Break the while loop when speed exceeds 80
  if (speed > 80) {
    break
  }
  
  if (speed > 48) {
    print("Slow down big time!")
    speed <- speed - 11
  } else {
    print("Slow down!")
    speed <- speed - 6
  }
}
```

```{r}
# Initialize the speed variable
Temperatura <- 120

while (Temperatura > 30) {
  print(paste("La temperatura es", Temperatura))
  
  if (Temperatura > 100) {
    print("No es posible disminuir la temperatura")
    break
  }
  
  if (Temperatura > 70) {
    print("La temperatura es muy alta")
    Temperatura <- Temperatura - 11
  } else {
    print("Bajando temperatura")
    Temperatura <- Temperatura - 6
  }
}
```




3.0.4 Build a while loop from scratch

```{r}
# Initialize i as 1 
i <- 1

# Code the while loop
while (i <= 10) {
  print(3 * i)
  if ( (3 * i) %% 8 == 0) {
    break
  }
  i <- i + 1
}
```

```{r}
Tablas <- 1

while (Tablas <= 10) {
  print(5 * Tablas)
  if ((5 * Tablas) %% 50 == 0) {
    break
  }
  Tablas <- Tablas + 1
}
```



3.0.5 Loop over a vector

```{r}
primes <- c(2, 3, 5, 7, 11, 13)

# loop version 1
for (p in primes) {
  print(p)
}

# loop version 2
for (i in 1:length(primes)) {
  print(primes[i])
}
```

```{r}
# The linkedin vector has already been defined for you
linkedin <- c(16, 9, 13, 5, 2, 17, 14)

# Loop version 1
for (li in linkedin) {
  print(li)
}
```




3.0.6 Loop over a list

```{r}

primes_list <- list(2, 3, 5, 7, 11, 13)

# loop version 1
for (p in primes_list) {
  print(p)
}

# loop version 2
for (i in 1:length(primes_list)) {
  print(primes_list[[i]])
}
```

```{r}
# The nyc list is already specified
nyc <- list(pop = 8405837, 
            boroughs = c("Manhattan", "Bronx", "Brooklyn", "Queens", "Staten Island"), 
            capital = FALSE)

# Loop version 1
for (info in nyc) {
  print(info)
}
```




3.0.7 Loop over a matrix

```{r}
# The tic-tac-toe matrix ttt has already been defined for you
d1 <- c("O",  "NA",   "X")
d2 <- c("NA", "O",  "O" )
d3 <- c("X",  "NA",  "X")

ttt_data <- c(d1, d2, d3)
ttt_data
```

```{r}
ttt <- matrix(ttt_data, byrow = TRUE, nrow = 3)
ttt
```

```{r}
# define the double for loop
for (i in 1:nrow(ttt)) {
  for (j in 1:ncol(ttt)) {
    print(paste("On row", i, "and column", j, "the board contains", ttt[i,j]))
  }
}
```




3.0.8 Mix it up with control flow

```{r}
# The linkedin vector has already been defined for you
linkedin <- c(16, 9, 13, 5, 2, 17, 14)

# Code the for loop with conditionals
for (li in linkedin) {
  if (li > 10) {
    print("You're popular!")
  } else {
    print("Be more visible!")
  }
  print(li)
}
```

```{r}
Tienda <- c(150, 200, 230, 180, 300)

for (Ga in Tienda) {
  if (Ga >= 200){
    print("Buenas ganancias en el día")
  } else {
    print("No hubo buenas ganancias")
  }
  print(Ga)
}
```




3.0.9 Next, you break it

```{r}
# The linkedin vector has already been defined for you
linkedin <- c(16, 9, 13, 5, 2, 17, 14)

# Adapt/extend the for loop
for (li in linkedin) {
  if (li > 10) {
    print("You're popular!")
  } else {
    print("Be more visible!")
  }
  
  # Add if statement with break
  if (li > 16) {
    print("This is ridiculous, I'm outta here!")
    break
  }
  
  # Add if statement with next
  if (li < 5) {
    print("This is too embarrassing!")
    next
  }
  
  print(li)
}
```




3.0.10 Build a for loop from scratch

```{r}
# Pre-defined variables
rquote <- "r's internals are irrefutably intriguing"
rquote

chars <- strsplit(rquote, split = "")[[1]]
chars

# Initialize rcount
rcount <- 0

# Finish the for loop
for (char in chars) {
  if (char == "r") {
    rcount <- rcount + 1
  }
  if (char == "u") {
    break
  }
}

# Print out rcount
rcount

```

```{r}
Nom <- "Gonzalo Chavira Campos"

Let <- strsplit(Nom, split = "")[[1]]

Cont <- 0

for (Letr in Let) {
  if (Letr == "a"){
    Cont <- Cont + 1
  }
  if (Letr == "s") {
    break
  }
}

Cont
```








4 Functions

4.0.1 Function documentation

```{r}
# Consult the documentation on the mean() function
?mean
help(mean)

# Inspect the arguments of the mean() function
args(mean)
```



4.0.2 Use a function

```{r}
# The linkedin and facebook vectors have already been created for you
linkedin <- c(16, 9, 13, 5, 2, 17, 14)
facebook <- c(17, 7, 5, 16, 8, 13, 14)

# Calculate average number of views
avg_li <- mean(linkedin)
avg_fb <- mean(facebook)

# Inspect avg_li and avg_fb
avg_li
```

```{r}
PromT1 <- mean(Tienda)

PromT1
```



4.0.3 Use a function (2)

```{r}
# The linkedin and facebook vectors have already been created for you
linkedin <- c(16, 9, 13, 5, 2, 17, 14)
facebook <- c(17, 7, 5, 16, 8, 13, 14)

# Calculate the mean of the sum
avg_sum <- mean(linkedin + facebook)

# Calculate the trimmed mean of the sum
avg_sum_trimmed <- mean(linkedin + facebook, trim = 0.2)

# Inspect both new variables
avg_sum
```



4.0.4 Use a function (3)

```{r}
linkedin <- c(16, 9, 13, 5, NA, 17, 14)
facebook <- c(17, NA, 5, 16, 8, 13, 14)

# Basic average of linkedin
mean(linkedin)

# Advanced average of linkedin
mean(linkedin, na.rm = TRUE)
```



4.0.5 Functions inside functions

```{r}
# The linkedin and facebook vectors have already been created for you
linkedin <- c(16, 9, 13, 5, NA, 17, 14)
facebook <- c(17, NA, 5, 16, 8, 13, 14)

# Calculate the mean absolute deviation
mean(abs(linkedin - facebook), na.rm = TRUE)
```



4.0.6 Write your own function

```{r}
# Create a function pow_two()
pow_two <- function(x) {
  x ^ 2
}

# Use the function
pow_two(12)
```

```{r}
Cuadrado <- function(x) {
  x ^ 4
}

Cuadrado(5)
```



4.0.7 Write your own function (2)

```{r}
# Define the function hello()
hello <- function() {
  print("Hi there!")
  TRUE
}

# Call the function hello()
hello()
```

```{r}
Saludo <- function() {
  print("Buenas noches")
  TRUE
}

Saludo()
```



4.0.9 R you functional?

```{r}
# The linkedin and facebook vectors have already been created for you
linkedin <- c(16, 9, 13,  5, 2, 17, 14)
facebook <- c(17, 7, 5, 16,  8, 13, 14)

# Define the interpret function
interpret <- function(num_views) {
  if (num_views > 15) {
    print("You're popular!")
    return(num_views)
  } else {
    print("Try to be more visible!")
    return(0)
  }
}

# Call the interpret function twice
interpret(linkedin[1])
```

```{r}
interpret <- function(Ganancias) {
  if (Ganancias -> 200){
    print("Buenas ganancias")
    return(Ganancias)
  } else {
    print("Malas ganancias")
    return(0)
  }
}

interpret(Tienda[3])
```



4.0.10 R you functional? (2)

```{r}
# The linkedin and facebook vectors have already been created for you
linkedin <- c(16, 9, 13, 5, 2, 17, 14)
facebook <- c(17, 7, 5, 16, 8, 13, 14)

# The interpret() can be used inside interpret_all()
interpret <- function(num_views) {
  if (num_views > 15) {
    print("You're popular!")
    return(num_views)
  } else {
    print("Try to be more visible!")
    return(0)
  }
}

# Define the interpret_all() function
# views: vector with data to interpret
# return_sum: return total number of views on popular days?
interpret_all <- function(views, return_sum = TRUE) {
  count <- 0

  for (v in views) {
    count <- count + interpret(v)
  }

  if (return_sum) {
    return(count)
  } else {
    return(NULL)
  }
}

# Call the interpret_all() function on both linkedin and facebook
interpret_all(linkedin)
```



4.0.11 Load an R Package

```{r}
# Load the ggplot2 package
library("ggplot2")

# Retry the qplot() function
qplot(mtcars$wt, mtcars$hp)
```

```{r}
# Check out the currently attached packages again
search()
```






5 The apply family

5.0.1 Use lapply with a built-in R functio

```{r}
# The vector pioneers has already been created for you
pioneers <- c("GAUSS:1777", "BAYES:1702", "PASCAL:1623", "PEARSON:1857")

# Split names from birth year
split_math <- strsplit(pioneers, split = ":")
split_math
```

```{r}
# Convert to lowercase strings: split_low
split_low <- lapply(split_math, tolower)
split_low
```

```{r}
# Take a look at the structure of split_low
str(split_low)
```




5.0.2 Use lapply with your own function

```{r}
# Write function select_first()
select_first <- function(x) {
  x[1]
}

# Apply select_first() over split_low: names
names <- lapply(split_low, select_first)
names
```
```{r}
# Write function select_second()
select_second <- function(x) {
  x[2]
}

# Apply select_second() over split_low: years
years <- lapply(split_low, select_second)
years
```




5.0.3 lapply and anonymous functions

```{r}
# Named function
triple <- function(x) { 3 * x }

# Anonymous function with same implementation
function(x) { 3 * x }

# Use anonymous function inside lapply()
lapply(list(1,2,3), function(x) { 3 * x })
```




5.0.4 Use lapply with additional arguments

```{r}
# Definition of split_low
pioneers <- c("GAUSS:1777", "BAYES:1702", "PASCAL:1623", "PEARSON:1857")
split <- strsplit(pioneers, split = ":")
split_low <- lapply(split, tolower)

# Generic select function
select_el <- function(x, index) {
  x[index]
}

# Use lapply() twice on split_low: names and years
names <- lapply(split_low, select_el, index = 1)
names

years <- lapply(split_low, select_el, index = 2)
years
```



5.0.5 How to use sapply

```{r}
# temp has already been defined in the workspace
# The tic-tac-toe matrix ttt has already been defined for you
t1 <- c( 3,  7,  9,  6, -1)
t2 <- c( 6,  9, 12, 13,  5)
t3 <- c(4,  8,  3, -1, -3)
t4 <- c(1,  4,  7,  2, -2)
t5 <- c(5, 7, 9, 4, 2)
t6 <- c(-3,  5,  8,  9,  4)
t7 <- c(3, 6, 9, 4, 1)


temp <- list(t1, t2, t3, t4, t5, t6, t7)
temp
```

```{r}
# Use lapply() to find each day's minimum temperature
lapply(temp, min)
```

```{r}
# Use sapply() to find each day's minimum temperature
sapply(temp, min)
```






5.0.6 sapply with your own function

```{r}
# temp is already defined in the workspace

# Finish function definition of extremes_avg
extremes_avg <- function(x) {
  ( min(x) + max(x) ) / 2
}

# Apply extremes_avg() over temp using sapply()
sapply(temp, extremes_avg)

# Apply extremes_avg() over temp using lapply()
lapply(temp, extremes_avg)
```




5.0.7 sapply with function returning vector

```{r}
# temp is already available in the workspace

# Create a function that returns min and max of a vector: extremes
extremes <- function(x) {
  c(min = min(x), max = max(x))
}

# Apply extremes() over temp with sapply()
sapply(temp, extremes)

lapply(temp, extremes)
```



5.0.8 sapply can’t simplify, now what?

```{r}
# temp is already prepared for you in the workspace

# Definition of below_zero()
below_zero <- function(x) {
  return(x[x < 0])
}

# Apply below_zero over temp using sapply(): freezing_s
freezing_s <- sapply(temp, below_zero)
freezing_s

# Apply below_zero over temp using lapply(): freezing_l
freezing_l <- lapply(temp, below_zero)
freezing_l

# Are freezing_s and freezing_l identical?
identical(freezing_s, freezing_l)
```



5.0.9 sapply with functions that return NULL

```{r}
# temp is already available in the workspace

# Definition of print_info()
print_info <- function(x) {
  cat("The average temperature is", mean(x), "\n")
}

# Apply print_info() over temp using sapply()
sapply(temp, print_info)

# Apply print_info() over temp using lapply()
lapply(temp, print_info)
```



5.0.10 Use vapply

```{r}
# temp is already available in the workspace

# Definition of basics()
basics <- function(x) {
  c(min = min(x), mean = mean(x), max = max(x))
}

# Apply basics() over temp using vapply()
vapply(temp, basics, numeric(3))
```


5.0.11 Use vapply (2

```{r}
# Definition of the basics() function
# basics <- function(x) {
#   c(min = min(x), mean = mean(x), median = median(x), max = max(x))
# }

# Fix the error:
#vapply(temp, basics, numeric(3))



# temp is already available in the workspace

# Definition of the basics() function
basics <- function(x) {
  c(min = min(x), mean = mean(x), median = median(x), max = max(x))
}

# Fix the error:
vapply(temp, basics, numeric(4))
```



5.0.12 From sapply to vapply

```{r}
# temp is already defined in the workspace

# Convert to vapply() expression
vapply(temp, max, numeric(1))

# Convert to vapply() expression
vapply(temp, function(x, y) { mean(x) > y }, logical(1), y = 5)
```







6 Utilities

6.0.1 Mathematical utilities

```{r}
# The errors vector has already been defined for you
errors <- c(1.9, -2.6, 4.0, -9.5, -3.4, 7.3)

# Sum of absolute rounded values of errors
sum(abs(round(errors)))
```



6.0.2 Find the error

```{r}
# Don't edit these two lines
vec1 <- c(1.5, 2.5, 8.4, 3.7, 6.3)
vec2 <- rev(vec1)

# Fix the error
#mean(abs(vec1), abs(vec2))

# Fix the error
mean(c(abs(vec1), abs(vec2)))
```



6.0.3 Data Utilities

```{r}
linkedin <- list(16, 9, 13, 5, 2, 17, 14)
linkedin

facebook <- list(17, 7, 5, 16, 8, 13, 14)
facebook

# Convert linkedin and facebook to a vector: li_vec and fb_vec
li_vec <- unlist(linkedin)
li_vec

fb_vec <- unlist(facebook)
fb_vec

# Append fb_vec to li_vec: social_vec
social_vec <- append(li_vec, fb_vec)
social_vec

# Sort social_vec
sort(social_vec, decreasing = TRUE)
```

```{r}
Tienda1 <- list(150, 250, 200, 180, 320)

Tienda2 <- list(230, 315, 190, 200, 270)

T1_vec <- unlist(Tienda1)
T2_vec <- unlist(Tienda2)

Tiendas_vec <- append(T1_vec, T2_vec)

sort(Tiendas_vec, decreasing = FALSE)
```



6.0.4 Find the error (2)

```{r}
# Fix me
#seq(rep(1, 7, by = 2), times = 7)

# Fix me
rep(seq(1, 7, by = 2), times = 7)
```

```{r}
rep(seq(1, 100, by = 8), times = 2)
```



6.0.5 Beat Gauss using R

```{r}
# Create first sequence: seq1
seq1 <- seq(1, 500, by = 3)
seq1

# Create second sequence: seq2
seq2 <- seq(1200, 900, by = -7)
seq2

sum(seq1) + sum(seq2)
```



6.0.6 grepl & grep

```{r}
# The emails vector has already been defined for you
emails <- c("john.doe@ivyleague.edu", "education@world.gov", "dalai.lama@peace.org",
            "invalid.edu", "quant@bigdatacollege.edu", "cookie.monster@sesame.tv")

# Use grepl() to match for "edu"
grepl("edu", emails)


# Use grep() to match for "edu", save result to hits
hits <- grep("edu", emails)
hits

# Subset emails using hits
emails[hits]
```




6.0.8 sub & gsub

```{r}
# The emails vector has already been defined for you
emails <- c("john.doe@ivyleague.edu", "education@world.gov", "global@peace.org",
            "invalid.edu", "quant@bigdatacollege.edu", "cookie.monster@sesame.tv")

# Use sub() to convert the email domains to datacamp.edu
sub("@.*\\.edu$", "@datacamp.edu", emails)
```

```{r}
Correos <- c("al122334@alumnos.uacj.mx", "al134351@alumnos.uacj.mx", "al113425@alumnos.utcj.mx", "al164712@alumnos.uacj.mx", "al153764@alumnos.utcj.mx")

sub("@.*\\.uacj.mx$", "@alumnos.uacjcu.mx", Correos)
```




6.0.10 Right here, right now

```{r}
# Get the current date: today
today <- Sys.Date()
today

# See what today looks like under the hood
unclass(today)


# Get the current time: now
now <- Sys.time()
now

# See what now looks like under the hood
unclass(now)
```



6.0.11 Create and format dates

```{r}
as.Date("1982-01-13")
as.Date("Jan-13-82", format = "%b-%d-%y")
as.Date("13 January, 1982", format = "%d %B, %Y")


today <- Sys.Date()
format(Sys.Date(), format = "%d %B, %Y")
format(Sys.Date(), format = "Today is a %A!")


# Definition of character strings representing dates
str1 <- "May 23, '96"
str2 <- "2012-03-15"
str3 <- "30/January/2006"

# Convert the strings to dates: date1, date2, date3
date1 <- as.Date(str1, format = "%b %d, '%y")
date1

date2 <- as.Date(str2)
date2

date3 <- as.Date(str3, format = "%d/%B/%Y")
date3

# Convert dates to formatted strings
format(date1, "%A")

format(date2, "%d")

format(date3, "%b %Y")
```




6.0.12 Create and format times

```{r}
# Definition of character strings representing times
str1 <- "May 23, '96 hours:23 minutes:01 seconds:45"
str2 <- "2012-3-12 14:23:08"

# Convert the strings to POSIXct objects: time1, time2
time1 <- as.POSIXct(str1, format = "%B %d, '%y hours:%H minutes:%M seconds:%S")
time1


time2 <- as.POSIXct(str2)
time2


# Convert times to formatted strings
format(time1, "%M")


format(time2, "%I:%M %p")
```

