---
title: "R Notebook"
output: html_notebook
---



2.1 Arithmetic with R

Addition: Con esta operacion podemos sumar valores. Un ejemplo de esto seria el siguiente:

```{r}
10 + 25

```


Subtraction: Con esta operacion podemos restar valores. 

```{r}
54 - 23
```

Multiplication: Con esta operacion podemos multiplicar los valores.

```{r}
14 * 2
```


Division: Con esta operacion podemos dividir los valores.

```{r}
25 / 5
```


Exponentiation: Esta operacion nos sirve para elevar los valores.

```{r}
5 ^ 4
```


Modulo: Esta operacion es para mostrar el residuo de la division del numero de la izquierda entre el numero de la derecha.

```{r}
10 %% 4
```



2.2 Variable assignment


Para asignar un valor a una variable primero tenemos que poner el nombre de la variable del lado izquierdo seguido de <- y el valor de la variable. Un ejemplo de esto:

```{r}
variable <- 66
```


Para imprimir el valor de la variable tecleamos print() y el valor de la variable:
```{r}
print(variable)
```



2.3 Variable assignment (2)

```{r}
# Assign the value 5 to the variable my_apples
my_apples <- 5


# Print out the value of the variable my_apples
my_apples
```

```{r}
Cheetos <- 12

Cheetos
```



2.4 Variable assignment (3)

```{r}
# Assign a value to the variables my_apples and my_oranges
my_apples  <- 5
my_oranges <- 6

# Add these two variables together
my_apples + my_oranges
```

```{r}
Cheetos <- 12
Doritos <- 16


Cheetos + Doritos
```


```{r}
# Create the variable my_fruit
my_fruit <- my_apples + my_oranges
```

```{r}
Papitas <- Cheetos + Doritos
```

··········································································

2.5 Apples and oranges

```{r}
# Assign a value to the variable my_apples
my_apples <- 5 

# Fix the assignment of my_oranges
my_oranges <- "six" 

# Create the variable my_fruit and print it out
#my_fruit <- my_apples + my_oranges 
##Error: non-numeric argument to binary operator

#my_fruit
##Error: object 'my_fruit' not found

# Fix the assignment of my_oranges
my_oranges <- 6

# Create the variable my_fruit and print it out
my_fruit <- my_apples + my_oranges 
my_fruit
```

```{r}
Cheetos <- 12

Doritos <-"Siete"

#Papita <- Cheetos + Doritos

#Error in Cheetos + Doritos : non-numeric argument to binary operator
```

```{r}
Papita
```
```{r}
Doritos <- 16

Papita <- Cheetos + Doritos 

Papita
```


··········································································


2.6 Basic data types in R

```{r}
# Change my_numeric to be 42
my_numeric <- 42

# Change my_character to be "universe"
my_character <- "universe"

# Change my_logical to be FALSE
my_logical <- FALSE
```

```{r}
Numerico <- 50

Caracter <- "Gonzalo"

Logico <- TRUE 
```


··········································································

2.7 What’s that data type?

```{r}
# Declare variables of different types:
my_numeric <- 42
my_character <- "universe"
my_logical <- FALSE

# Check class of my_numeric
class(my_numeric)
```

```{r}
Numerico <- 50

Caracter <- "Gonzalo"

Logico <- TRUE 
```

```{r}
class(Caracter)
```



··········································································
Chapter 3 Vectors

```{r}
numeric_vector <- c(1, 10, 49)
character_vector <- c("a", "b", "c")

# Complete the code for boolean_vector
boolean_vector <- c(TRUE, FALSE, TRUE)
```

```{r}
Vector_numerico <- c(12, 25, 34)

Vector_caracter <- c("g", "z", "o")

Vector_booleano <-c(FALSE, FALSE, FALSE)
```



3.3 Create a vector (3)

```{r}
# Poker winnings from Monday to Friday
poker_vector <- c(140, -50, 20, -120, 240)

# Roulette winnings from Monday to Friday
roulette_vector <- c(-24, -50, 100, -350, 10)
```

```{r}
#Ganancias de dos semanas de una tienda

#Semana 1
semana1_vector <- c(300, 450, -200, 380, -100, 250, 510)

#Semana 2 
semana2_vector <- c(-100, 310, 440, 280, 520, -50, 420)

```


3.4 Naming a vector

```{r}
# Poker winnings from Monday to Friday
poker_vector <- c(140, -50, 20, -120, 240)

# Roulette winnings from Monday to Friday
roulette_vector <- c(-24, -50, 100, -350, 10)

# The variable days_vector
days_vector <- c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday")

# Assign the names of the day to roulette_vector and poker_vector
names(poker_vector) <- days_vector
names(roulette_vector) <- days_vector
```

```{r}
#Ganancias de dos semanas de una tienda

#Semana 1
semana1_vector <- c(300, 450, -200, 380, -100, 250, 510)

#Semana 2 
semana2_vector <- c(-100, 310, 440, 280, 520, -50, 420)

#Vector de dias de la semana
dias_vector <- c("Lunes", "Martes", "Miercoles", "Jueves", "Viernes", "Sabado", "Domingo")

names(semana1_vector) <- dias_vector
names(semana2_vector) <- dias_vector
```


3.6 Calculating total winnings

```{r}
# Poker and roulette winnings from Monday to Friday:
poker_vector <- c(140, -50, 20, -120, 240)
roulette_vector <- c(-24, -50, 100, -350, 10)
days_vector <- c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday")
names(poker_vector) <- days_vector
names(roulette_vector) <- days_vector

# Assign to total_daily how much you won/lost on each day
total_daily <- poker_vector + roulette_vector
total_daily
```

```{r}
#Ganancias de dos semanas de una tienda

#Semana 1
semana1_vector <- c(300, 450, -200, 380, -100, 250, 510)

#Semana 2 
semana2_vector <- c(-100, 310, 440, 280, 520, -50, 420)

#Vector de dias de la semana
dias_vector <- c("Lunes", "Martes", "Miercoles", "Jueves", "Viernes", "Sabado", "Domingo")

names(semana1_vector) <- dias_vector
names(semana2_vector) <- dias_vector

total_diario <- semana1_vector + semana2_vector
total_diario
```

3.8 Calculating total winnings (3)

```{r}
# Poker and roulette winnings from Monday to Friday:
poker_vector <- c(140, -50, 20, -120, 240)
roulette_vector <- c(-24, -50, 100, -350, 10)
days_vector <- c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday")
names(poker_vector) <- days_vector
names(roulette_vector) <- days_vector

# Total winnings with poker
total_poker <- sum(poker_vector)
total_poker
```

```{r}
total_semana1 <- sum(semana1_vector)
total_semana1

total_semana2 <- sum(semana2_vector)
total_semana2

total_semanas <- total_semana1 + total_semana2
total_semanas
```


3.9 Comparing total winnings

```{r}
# Check if you realized higher total gains in poker than in roulette
total_poker > total_roulette
```

```{r}
#Checamos si el total de la semana 1 es mayor al total de la semana 2
total_semana1 > total_semana2
```



3.10 Vector selection: the good times

```{r}
# Poker and roulette winnings from Monday to Friday:
poker_vector <- c(140, -50, 20, -120, 240)
roulette_vector <- c(-24, -50, 100, -350, 10)
days_vector <- c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday")
names(poker_vector) <- days_vector
names(roulette_vector) <- days_vector

# Define a new variable based on a selection
poker_wednesday <- poker_vector[3]
poker_wednesday
```

```{r}
#Ganancias de dos semanas de una tienda

#Semana 1
semana1_vector <- c(300, 450, -200, 380, -100, 250, 510)

#Semana 2 
semana2_vector <- c(-100, 310, 440, 280, 520, -50, 420)

#Vector de dias de la semana
dias_vector <- c("Lunes", "Martes", "Miercoles", "Jueves", "Viernes", "Sabado", "Domingo")

names(semana1_vector) <- dias_vector
names(semana2_vector) <- dias_vector

# Definimos las ganancias del viernes de la semana 1 en una variable
semana1_viernes <- semana1_vector[5]

semana1_viernes
```


3.11 Vector selection: the good times (2)

```{r}
# Poker and roulette winnings from Monday to Friday:
poker_vector <- c(140, -50, 20, -120, 240)
roulette_vector <- c(-24, -50, 100, -350, 10)
days_vector <- c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday")
names(poker_vector) <- days_vector
names(roulette_vector) <- days_vector

# Define a new variable based on a selection
poker_midweek <- poker_vector[c(2, 3, 4)]
poker_midweek



#Ganancias de dos semanas de una tienda
#Semana 1
semana1_vector <- c(300, 450, -200, 380, -100, 250, 510)

#Semana 2 
semana2_vector <- c(-100, 310, 440, 280, 520, -50, 420)

#Vector de dias de la semana
dias_vector <- c("Lunes", "Martes", "Miercoles", "Jueves", "Viernes", "Sabado", "Domingo")

names(semana1_vector) <- dias_vector
names(semana2_vector) <- dias_vector


#Hacemos una variable para las ganancias del fin de semana

semana1_finde <- semana1_vector[c(5, 6, 7)]
semana1_finde
```


3.12 Vector selection: the good times (3)

```{r}
# Poker and roulette winnings from Monday to Friday:
poker_vector <- c(140, -50, 20, -120, 240)
roulette_vector <- c(-24, -50, 100, -350, 10)
days_vector <- c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday")
names(poker_vector) <- days_vector
names(roulette_vector) <- days_vector

# Define a new variable based on a selection
roulette_selection_vector <- roulette_vector[2:5]
roulette_selection_vector


# Ganancias de lunes a viernes de la semana 1 
lunvie_semana1 <- semana1_vector [1:5]
lunvie_semana1
```


3.13 Vector selection: the good times (4)

```{r}
# Poker and roulette winnings from Monday to Friday:
poker_vector <- c(140, -50, 20, -120, 240)
roulette_vector <- c(-24, -50, 100, -350, 10)
days_vector <- c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday")
names(poker_vector) <- days_vector
names(roulette_vector) <- days_vector

# Select poker results for Monday, Tuesday and Wednesday
poker_start <- poker_vector[c("Monday", "Tuesday", "Wednesday")]
poker_start
```

```{r}
#Ganancias de dos semanas de una tienda
#Semana 1
semana1_vector <- c(300, 450, -200, 380, -100, 250, 510)

#Semana 2 
semana2_vector <- c(-100, 310, 440, 280, 520, -50, 420)

#Vector de dias de la semana
dias_vector <- c("Lunes", "Martes", "Miercoles", "Jueves", "Viernes", "Sabado", "Domingo")

names(semana1_vector) <- dias_vector
names(semana2_vector) <- dias_vector


# Seleccionamos las ganancias de la semana poniendo los dias 
gandias_semana1 <- semana1_vector [c("Lunes", "Jueves", "Domingo")]
gandias_semana1

# Promedio de los dias seleccionados
mean(gandias_semana1)
```


3.14 Selection by comparison - Step 1

```{r}
# Poker and roulette winnings from Monday to Friday:
poker_vector <- c(140, -50, 20, -120, 240)
roulette_vector <- c(-24, -50, 100, -350, 10)
days_vector <- c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday")
names(poker_vector) <- days_vector
names(roulette_vector) <- days_vector

# Which days did you make money on poker?
selection_vector <- poker_vector > 0
  
# Print out selection_vector
selection_vector
```

```{r}
#Ganancias de dos semanas de una tienda
#Semana 1
semana1_vector <- c(300, 450, -200, 380, -100, 250, 510)

#Semana 2 
semana2_vector <- c(-100, 310, 440, 280, 520, -50, 420)

#Vector de dias de la semana
dias_vector <- c("Lunes", "Martes", "Miercoles", "Jueves", "Viernes", "Sabado", "Domingo")

names(semana1_vector) <- dias_vector
names(semana2_vector) <- dias_vector


# Seleccionamos en cuales dias hubo perdidas 

perdidas_semana1 <- semana1_vector < 0

perdidas_semana1
```


3.15 Selection by comparison - Step 2

```{r}
# Poker and roulette winnings from Monday to Friday:
poker_vector <- c(140, -50, 20, -120, 240)
roulette_vector <- c(-24, -50, 100, -350, 10)
days_vector <- c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday")
names(poker_vector) <- days_vector
names(roulette_vector) <- days_vector

# Which days did you make money on poker?
selection_vector <- poker_vector > 0
selection_vector

# Select from poker_vector these days
poker_winning_days <- poker_vector[selection_vector]
poker_winning_days
```

```{r}
#Ganancias de dos semanas de una tienda
#Semana 1
semana1_vector <- c(300, 450, -200, 380, -100, 250, 510)

#Semana 2 
semana2_vector <- c(-100, 310, 440, 280, 520, -50, 420)

#Vector de dias de la semana
dias_vector <- c("Lunes", "Martes", "Miercoles", "Jueves", "Viernes", "Sabado", "Domingo")

names(semana1_vector) <- dias_vector
names(semana2_vector) <- dias_vector


# Dias en que hubo perdidas en la semana 1
diasperdidas_semana1 <- semana1_vector[perdidas_semana1]

diasperdidas_semana1 
```


3.16 Advanced selection

```{r}
# Poker and roulette winnings from Monday to Friday:
poker_vector <- c(140, -50, 20, -120, 240)
roulette_vector <- c(-24, -50, 100, -350, 10)
days_vector <- c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday")
names(poker_vector) <- days_vector
names(roulette_vector) <- days_vector

# Which days did you make money on roulette?
selection_vector <- roulette_vector > 0
selection_vector


# Select from roulette_vector these days
roulette_winning_days <- roulette_vector[selection_vector]
roulette_winning_days
```

```{r}
#Ganancias de dos semanas de una tienda
#Semana 1
semana1_vector <- c(300, 450, -200, 380, -100, 250, 510)

#Semana 2 
semana2_vector <- c(-100, 310, 440, 280, 520, -50, 420)

#Vector de dias de la semana
dias_vector <- c("Lunes", "Martes", "Miercoles", "Jueves", "Viernes", "Sabado", "Domingo")

names(semana1_vector) <- dias_vector
names(semana2_vector) <- dias_vector

ganancias_semana2 <- semana2_vector > 0
ganancias_semana2 

# Dias en que hubo ganancias en la semana 2 
diasgan_semana2 <- semana2_vector[ganancias_semana2]
diasgan_semana2
```





··········································································
Chapter 4 Matrices



4.1 What’s a matrix?

```{r}
# Construct a matrix with 3 rows that contain the numbers 1 up to 9
matrix(1:9, byrow = TRUE, nrow = 3)
```

```{r}
#Creamos una matriz con numeros del 1 al 20 con 4 filas
matrix(1:20, byrow = TRUE, nrow = 4)
```


4.2 Analyze matrices, you shall

```{r}
# Box office Star Wars (in millions!)
new_hope <- c(460.998, 314.4)
empire_strikes <- c(290.475, 247.900)
return_jedi <- c(309.306, 165.8)

# Create box_office
box_office <- c(new_hope, empire_strikes, return_jedi)
box_office

# Construct star_wars_matrix
star_wars_matrix <- matrix(box_office, nrow = 3, byrow = TRUE) 
star_wars_matrix
```

```{r}
# Ganancias mensuales de 3 supermercados 
Smart <- c(20.100, 15.400)
Soriana <- c(18.400, 19.200)
Walmart <- c(17.800, 22.300)

GananciasSM <- c(Smart, Soriana, Walmart)
GananciasSM

GananciasSM_Matriz <- matrix(GananciasSM, nrow = 3, byrow = TRUE)
GananciasSM_Matriz
```


4.3 Naming a matrix

```{r}
# Box office Star Wars (in millions!)
new_hope <- c(460.998, 314.4)
empire_strikes <- c(290.475, 247.900)
return_jedi <- c(309.306, 165.8)

# Construct matrix
star_wars_matrix <- matrix(c(new_hope, empire_strikes, return_jedi), nrow = 3, byrow = TRUE)

# Vectors region and titles, used for naming
region <- c("US", "non-US")
titles <- c("A New Hope", "The Empire Strikes Back", "Return of the Jedi")

# Name the columns with region
colnames(star_wars_matrix) <- region

# Name the rows with titles
rownames(star_wars_matrix) <- titles

# Print out star_wars_matrix
star_wars_matrix
```

```{r}
# Ganancias mensuales de 3 supermercados 
Smart <- c(20.100, 15.400)
Soriana <- c(18.400, 19.200)
Walmart <- c(17.800, 22.300)

GananciasSM_Matriz <- matrix(GananciasSM, nrow = 3, byrow = TRUE)

MesSM <- c("Junio", "Julio")
NombreSM <- c("Smart", "Soriana", "Walmart")

colnames(GananciasSM_Matriz) <- MesSM
rownames(GananciasSM_Matriz) <- NombreSM

GananciasSM_Matriz
```


4.4 Calculating the worldwide box office

```{r}
# Construct star_wars_matrix
box_office <- c(460.998, 314.4, 290.475, 247.900, 309.306, 165.8)
star_wars_matrix <- matrix(box_office, nrow = 3, byrow = TRUE,
                           dimnames = list(c("A New Hope", "The Empire Strikes Back", "Return of the Jedi"), 
                                           c("US", "non-US")))

# Calculate worldwide box office figures
worldwide_vector <- rowSums(star_wars_matrix)
worldwide_vector
```

```{r}
GananciasSM <- c(20.100, 15.400, 18.400, 19.200, 17.800, 22.300)
GananciasSM_Matriz <- matrix(GananciasSM, nnrow = 3, byrow = TRUE,
                             dimnames = list(c("Smart", "Soriana", "Walmart"), c("Junio","Julio")))

GananciasSM_Vector <- rowSums(GananciasSM_Matriz)
GananciasSM_Vector
```


4.5 Adding a column for the Worldwide box office

```{r}
# Construct star_wars_matrix
box_office <- c(460.998, 314.4, 290.475, 247.900, 309.306, 165.8)
star_wars_matrix <- matrix(box_office, nrow = 3, byrow = TRUE,
                           dimnames = list(c("A New Hope", "The Empire Strikes Back", "Return of the Jedi"), 
                                           c("US", "non-US")))

# The worldwide box office figures
worldwide_vector <- rowSums(star_wars_matrix)

# Bind the new variable worldwide_vector as a column to star_wars_matrix
all_wars_matrix <- cbind(star_wars_matrix, worldwide_vector)
all_wars_matrix
```

```{r}
GananciasSM <- c(20.100, 15.400, 18.400, 19.200, 17.800, 22.300)
GananciasSM_Matriz <- matrix(GananciasSM, nrow = 3, byrow = TRUE,
                             dimnames = list(c("Smart", "Soriana", "Walmart"), c("Junio","Julio")))

GananciasSM_Vector <- rowSums(GananciasSM_Matriz)

TodasGan_Matriz <- cbind(GananciasSM_Matriz, GananciasSM_Vector)
TodasGan_Matriz
```



4.6 Adding a row

```{r}
# Construct star_wars_matrix
box_office <- c(460.998, 314.4, 290.475, 247.900, 309.306, 165.8)
star_wars_matrix <- matrix(box_office, nrow = 3, byrow = TRUE,
                           dimnames = list(c("A New Hope", "The Empire Strikes Back", "Return of the Jedi"), 
                                           c("US", "non-US")))

# Construct star_wars_matrix2
box_office2 <- c(474.5, 552.5, 310.7, 338.7, 380.3, 468.5)
star_wars_matrix2 <- matrix(box_office2, nrow = 3, byrow = TRUE,
                           dimnames = list(c("The Phantom Menace", "Attack of the Clones", "Revenge of the Sith"), 
                                           c("US", "non-US")))


# Combine both Star Wars trilogies in one matrix
all_wars_matrix <- rbind(star_wars_matrix, star_wars_matrix2)
all_wars_matrix
```

```{r}
GananciasSM <- c(20.100, 15.400, 18.400, 19.200, 17.800, 22.300)
GananciasSM_Matriz <- matrix(GananciasSM, nrow = 3, byrow = TRUE,
                             dimnames = list(c("Smart", "Soriana", "Walmart"), c("Junio","Julio")))


GananciasSM2 <- c(10.100, 11.200, 9.000, 8.500, 7.800, 6.700)
GananciasSM_Matriz2 <- matrix(GananciasSM2, nrow = 3, byrow = TRUE,
                              dimnames = list(c("Aurrera", "Gonzales", "Superette"),
                                              c("Junio", "Julio")))

TodasGan_Matriz <- rbind(GananciasSM_Matriz, GananciasSM_Matriz2)
TodasGan_Matriz
```


4.7 The total box office revenue for the entire saga

```{r}
# all_wars_matrix is available in your workspace
all_wars_matrix


# Total revenue for US and non-US
total_revenue_vector <- colSums(all_wars_matrix)

# Print out total_revenue_vector
total_revenue_vector
```

```{r}
TodasGan_Matriz

Ingreso_Total_Vector <- colSums(TodasGan_Matriz)
Ingreso_Total_Vector
```


4.8 Selection of matrix elements

```{r}
# all_wars_matrix is available in your workspace
all_wars_matrix

# Select the non-US revenue for all movies
non_us_all <- all_wars_matrix[,2]
non_us_all

# Average non-US revenue
mean(non_us_all)

# Select the non-US revenue for first two movies
non_us_some <- all_wars_matrix[1:2,2]
non_us_some

# Average non-US revenue for first two movies
mean(non_us_some)
```

```{r}
TodasGan_Matriz

TodoJulio <- TodasGan_Matriz[, 2]
TodoJulio

mean(TodoJulio)


JulioTres <- TodasGan_Matriz[1:3, 2]
JulioTres

mean(JulioTres)
```


4.9 A little arithmetic with matrices

```{r}
# all_wars_matrix is available in your workspace
all_wars_matrix


# Estimate the visitors
visitors <- all_wars_matrix / 5

# Print the estimate to the console
visitors
```

```{r}
TodasGan_Matriz

Compradores <- TodasGan_Matriz / 1.2

Compradores
```


4.10 A little arithmetic with matrices (2)

```{r}
# all_wars_matrix and ticket_prices_matrix are available in your workspace
all_wars_matrix


# Construct ticket_prices
ticket_office <- c(5, 6, 7, 4, 4.5, 4.9)
ticket_prices1 <- matrix(ticket_office, nrow = 3, byrow = TRUE,
                           dimnames = list(c("A New Hope", "The Empire Strikes Back", "Return of the Jedi"), 
                                           c("US", "non-US")))

# Construct star_wars_matrix2
ticket_office2 <- c(5, 6, 7, 4, 4.5, 4.9)
ticket_prices2 <- matrix(ticket_office2, nrow = 3, byrow = TRUE,
                           dimnames = list(c("The Phantom Menace", "Attack of the Clones", "Revenge of the Sith"), 
                                           c("US", "non-US")))


# Combine both Star Wars trilogies in one matrix
ticket_prices_matrix <- rbind(ticket_prices1, ticket_prices2)
ticket_prices_matrix


# Estimated number of visitors
visitors <- all_wars_matrix / ticket_prices_matrix

# US visitors
us_visitors <- visitors[ ,1]
us_visitors


# Average number of US visitors
mean(us_visitors)
```




··········································································
Chapter 5 Factors


5.1 What’s a factor and why would you use it?

```{r}
# Sex vector
sex_vector <- c("Male", "Female", "Female", "Male", "Male")
sex_vector


# Convert sex_vector to a factor
factor_sex_vector <- factor(sex_vector)

# Print out factor_sex_vector
factor_sex_vector
```

```{r}
Edades_Vector <- c(18, 19, 18, 20, 20, 18)
Edades_Vector


Factor_Edades_Vector <- factor(Edades_Vector)
Factor_Edades_Vector
```


5.3 What’s a factor and why would you use it? (3)

```{r}
# Animals
animals_vector <- c("Elephant", "Giraffe", "Donkey", "Horse")
animals_vector

class(animals_vector)

factor_animals_vector <- factor(animals_vector)
factor_animals_vector


# Temperature
temperature_vector <- c("High", "Low", "High","Low", "Medium")
temperature_vector

factor_temperature_vector <- factor(temperature_vector, order = TRUE, levels = c("Low", "Medium", "High"))
factor_temperature_vector
```

```{r}
Volumen_Vector <- c("Alto", "Alto", "Bajo", "Medio", "Medio")
Volumen_Vector

Factor_Volumen_Vector <- factor(Volumen_Vector, order = TRUE, levels = c("Bajo", "Medio", "Alto"))
Factor_Volumen_Vector
```


5.4 Factor levels

```{r}
# Code to build factor_survey_vector
survey_vector <- c("M", "F", "F", "M", "M")
survey_vector

factor_survey_vector <- factor(survey_vector)
factor_survey_vector

# Specify the levels of factor_survey_vector
levels(factor_survey_vector) <- c("Female", "Male")

factor_survey_vector
```

```{r}
Encuesta_Vector <- c("F", "F", "M", "F", "M", "F")
Encuesta_Vector

Factor_Encuesta_Vector <- factor(Encuesta_Vector)
Factor_Encuesta_Vector

levels(Factor_Encuesta_Vector) <- c("Femenino", "Masculino")
Factor_Encuesta_Vector
```


5.5 Summarizing a factor

```{r}
# Build factor_survey_vector with clean levels
survey_vector <- c("M", "F", "F", "M", "M")
survey_vector

factor_survey_vector <- factor(survey_vector)

levels(factor_survey_vector) <- c("Female", "Male")

factor_survey_vector

# Generate summary for survey_vector
summary(survey_vector)

# Generate summary for factor_survey_vector
summary(factor_survey_vector)
```

```{r}
Encuesta_Vector <- c("F", "F", "M", "F", "M", "F")
Encuesta_Vector

Factor_Encuesta_Vector <- factor(Encuesta_Vector)
Factor_Encuesta_Vector

levels(Factor_Encuesta_Vector) <- c("Femenino", "Masculino")
Factor_Encuesta_Vector

summary(Encuesta_Vector)
summary(Factor_Encuesta_Vector)
```


5.6 Battle of the sexes

```{r}
# Build factor_survey_vector with clean levels
survey_vector <- c("M", "F", "F", "M", "M")
factor_survey_vector <- factor(survey_vector)
levels(factor_survey_vector) <- c("Female", "Male")

# Male
male <- factor_survey_vector[1]
male

# Female
female <- factor_survey_vector[2]
female

# Battle of the sexes: Male 'larger' than female?
male > female
```

```{r}
Encuesta_Vector <- c("F", "F", "M", "F", "M", "F")
Encuesta_Vector

Factor_Encuesta_Vector <- factor(Encuesta_Vector)
Factor_Encuesta_Vector

levels(Factor_Encuesta_Vector) <- c("Femenino", "Masculino")
Factor_Encuesta_Vector

Masculino <- Factor_Encuesta_Vector[1]
Masculino

Femenino <- Factor_Encuesta_Vector[2]
Femenino

Masculino < Femenino

## Warning in Ops.factor(male, female): '>' not meaningful for factors
## [1] NA
```


5.7 Ordered factors

```{r}
# Create speed_vector
speed_vector <- c("medium", "slow", "slow", "medium", "fast")
speed_vector
```

```{r}
#Velocidad de descarga 
Velocidad_Vector <- c("10mbps", "50mbps", "10mbps", "100mbps", "100mbps")
Velocidad_Vector
```


5.8 Ordered factors (2)

```{r}
# Create speed_vector
speed_vector <- c("medium", "slow", "slow", "medium", "fast")
speed_vector

# Add your code below
factor_speed_vector <- factor(speed_vector, ordered = TRUE, levels = c("slow", "medium", "fast"))

# Print factor_speed_vector
factor_speed_vector

summary(factor_speed_vector)
```

```{r}
#Velocidad de descarga 
Velocidad_Vector <- c("10mbps", "50mbps", "10mbps", "100mbps", "100mbps")
Velocidad_Vector

Factor_Velocidad_Vector <- factor(Velocidad_Vector, ordered = TRUE, levels = c("10mbps", "50mbps", "100mbps"))

Factor_Velocidad_Vector

summary(Factor_Velocidad_Vector)
```


5.9 Comparing ordered factors

```{r}
# Create factor_speed_vector
speed_vector <- c("medium", "slow", "slow", "medium", "fast")
factor_speed_vector <- factor(speed_vector, ordered = TRUE, levels = c("slow", "medium", "fast"))

# Factor value for second data analyst
da2 <- factor_speed_vector[2]
da2

# Factor value for fifth data analyst
da5 <- factor_speed_vector[5]
da5

# Is data analyst 2 faster data analyst 5?
da2 > da5
```

```{r}
#Velocidad de descarga 
Velocidad_Vector <- c("10mbps", "50mbps", "10mbps", "100mbps", "100mbps")
Velocidad_Vector

Factor_Velocidad_Vector <- factor(Velocidad_Vector, ordered = TRUE, levels = c("10mbps", "50mbps", "100mbps"))

da1 <- Factor_Velocidad_Vector[1]
da1

da2 <- Factor_Velocidad_Vector[2]
da2

da1 < da2
```





··········································································
Chapter 6 Data frames.

6.1 What’s a data frame?

```{r}
mtcars

class(mtcars)
```


6.2 Quick, have a look at your data set

```{r}
# Call head() on mtcars
head(mtcars)
```


6.3 Have a look at the structure

```{r}
# Investigate the structure of mtcars
str(mtcars)

```


6.4 Creating a data frame

```{r}
# Definition of vectors
name <- c("Mercury", "Venus", "Earth", "Mars", "Jupiter", "Saturn", "Uranus", "Neptune")
name


type <- c("Terrestrial planet", "Terrestrial planet", "Terrestrial planet", 
          "Terrestrial planet", "Gas giant", "Gas giant", "Gas giant", "Gas giant")
type


diameter <- c(0.382, 0.949, 1, 0.532, 11.209, 9.449, 4.007, 3.883)
diameter


rotation <- c(58.64, -243.02, 1, 1.03, 0.41, 0.43, -0.72, 0.67)
rotation


rings <- c(FALSE, FALSE, FALSE, FALSE, TRUE, TRUE, TRUE, TRUE)
rings


# Create a data frame from the vectors
planets_df <- data.frame(name, type, diameter, rotation, rings)
planets_df
```

```{r}
NombreAnim <- c("Lobo", "Aguila", "Tiburon", "Pulpo", "Perro", "Panda", "Elefante")
NombreAnim

TipoAnim <- c("Terrestre","Aereo", "Acuatico", "Acuatico", "Terrestre", "Terrestre", "Terrestre" )
TipoAnim

NacAnim <- c("Viviparo", "Oviparo", "Ovoviviparo", "Oviparo", "Viviparo", "Viviparo", "Viviparo")
NacAnim

PatasAnim <- c(TRUE, TRUE , FALSE, FALSE, TRUE, TRUE, TRUE)
PatasAnim

AliAnim <- c("Carnivoro", "Carnivoro", "Carnivoro", "Carnivoro", "Carnivoro", "Herbivoro", "Herbivoro")
AliAnim


Animales_Df <- data.frame(NombreAnim, TipoAnim, NacAnim, PatasAnim, AliAnim)
Animales_Df


class(Animales_Df)

str(Animales_Df)
```


6.6 Selection of data frame elements

```{r}
# The planets_df data frame from the previous exercise is pre-loaded

# Print out diameter of Mercury (row 1, column 3)
planets_df[1,3]

# Print out data for Mars (entire fourth row)
planets_df[4, ]
```

```{r}
Animales_Df[1, 2]
```


6.7 Selection of data frame elements (2)

```{r}
# The planets_df data frame from the previous exercise is pre-loaded

# Select first 5 values of diameter column
planets_df[1:5, "diameter"]
```

```{r}
Animales_Df[1:2, "TipoAnim"]
```


6.8 Only planets with rings

```{r}
# planets_df is pre-loaded in your workspace

# Select the rings variable from planets_df
rings_vector <- planets_df$rings

# Print out rings_vector
rings_vector
```

```{r}
Patas_Vector <- Animales_Df$PatasAnim

Patas_Vector
```


6.9 Only planets with rings (2)

```{r}
# planets_df and rings_vector are pre-loaded in your workspace

# Adapt the code to select all columns for planets with rings
planets_df[rings_vector, ]
```

```{r}
Animales_Df[Patas_Vector, ]
```


6.10 Only planets with rings but shorter

```{r}
# planets_df is pre-loaded in your workspace

# Select planets with diameter < 1
subset(planets_df, subset = diameter < 1)
```

```{r}
subset(Animales_Df, subset = AliAnim == "Herbivoro")
```


6.11 Sorting

```{r}
?order()
```


6.12 Sorting your data frame

```{r}
# planets_df is pre-loaded in your workspace

# Use order() to create positions
positions <- order(planets_df$diameter)
positions

# Use positions to sort planets_df
planets_df[positions, ]
```

```{r}
PosiNomAni <- order(Animales_Df$NombreAnim)
PosiNomAni

Animales_Df[PosiNomAni, ]
```





··········································································



