---
title: "R Notebook"
output: html_notebook
---

Q1. Using R as a calculator
Exercise 1: Calculate square root of 729

```{r}
sqrt (729)
```




Q2. Creating a numeric variable
Exercise 2: Create a new variable 'b' with value 1947.0

```{r}
b <- 1947.0
```




Q3. How to convert a numeric variable to character
Exercise 3: Convert 'b' from previous exercise to character

```{r}
b <- as.character(b)

print (b)
```




Q5. Create an environment within the global environment

Exercise 5.1: Create a new environment called 'myEnv'
```{r}
myEnv <- new.env()
```

Exercise 5.2: Create a variable inside it
```{r}
assign('b', 3, envir = myEnv)
```

Exercise 5.3: Access the variable inside the new environment
```{r}
get('b', envir=myEnv)
```

Exercise 5.4: Delete the variable inside that environment
```{r}
rm(b, envir=myEnv)
```




Q6. Create a numeric vector

Exercise 6.a: Create a vector numbers from 1 to 6 and find out its class
```{r}
one_to_six <- c(1, 2, 3, 4, 5, 6)

class(one_to_six)
```

Exercise 6.b: Create a vector containing following mixed elements {1, 'a', 2, 'b'} and find out its class
```{r}
one_a <- c(1, "a", 2, "b")

class(one_a) # character
```




Q7. Initialise Character vector


Exercise 7.a: Initialise a character vector of length 26
```{r}
charHundred <- character(26)

charHundred
```

Exercise 7.b: Assign the character 'a' to the first element in above vector.
```{r}
charHundred[1] <- "a"
```




Q8. Vector operations


Exercise 8.1: Create a vector with some of your friend's names
```{r}
MisAmigos <- c("Kike", "Agustin", "Sergio", "Roger", "Pillo")
```


Exercise 8.2: Get the length of above vector
```{r}
length(MisAmigos)
```


Exercise 8.3: Get the first two friends from above vector
```{r}
MisAmigos[1:2]
```


Exercise 8.4: Get the 2nd and 3rd friends
```{r}
MisAmigos[c(2,3)]
```


Exercise 8.5: Sort your friends by names using 2 methods
```{r}
sort(MisAmigos)

MisAmigos[order(MisAmigos)]
```


Exercise 8.6: Reverse direction of the above sort
```{r}
sort(MisAmigos, decreasing=TRUE)

MisAmigos[rev(order(MisAmigos))]
```





Q9. Create customised vector sequences

Exercise 9: Create with rep and seq: 'a','a',1,2,3,4,5,7,9,11
```{r}
# because of the presence of 'a' character, the numbers are converted to characters as well.
out <- c(rep('a', 2), seq(1, 5), seq(7, 11, by=2)) 
```





Q10. Remove missing values

Exercise 10: Remove missing value from c(1, 2, NA, 4)
```{r}
MiVector <- c(1, 2, NA, 4)
MiVector[!is.na(MiVector)]
```





Q11. Random sampling


Exercise 11: Pick 50 random numbers between 1 to 100, with replacement
```{r}
NumRandom <-sample(1:100, 50, replace=T)
NumRandom
```




Q12. Checking the class

Exercise 12: Check the class of mySample
```{r}
class (NumRandom) 
```





Q13. Find the class of ‘iris’ dataframe, find the class of all the columns of ‘iris’, get the summary of ‘iris’, get the top 6 rows, view it in a spreadsheet format, get row names, get column names, get number of rows and get number of columns.


Exercise 13: Apply the above functions and inspect results on 'iris' (a base R dataframe)
```{r}
class (iris)  # get class
```

```{r}
sapply (iris, class)  # get class of all columns
```

```{r}
str (iris)  # structure
```

```{r}
summary (iris)  # summary of airquality
```

```{r}
head (iris)  # view the first 6 obs
```

```{r}
fix (iris)  # view spreadsheet like grid
```

```{r}
rownames (iris)  # row names
```

```{r}
colnames (iris)  # columns names
```

```{r}
nrow (iris)  # number of rows
```

```{r}
ncol (iris)  # number of columns
```





Q14. Subsetting a dataframe

Exercise 14.1: Get the last 2 rows in last 2 columns from iris dataset
```{r}
numRows <- nrow(iris)

numCols <- ncol(iris)

iris[(numRows-1):numRows, (numCols-1):numCols]
```

Exercise 14.2: Get rows with Sepal.Width > 3.5 using which() from iris
```{r}
iris[iris$Sepal.Width > 3, ]

iris[which(iris$Sepal.Width > 3), ]
```

Exercise 14.3: Get the rows with 'versicolor' species using subset() from iris
```{r}
subset(iris, Species == "versicolor")
```






Q15. With the dataframes created from code below, perform the various merge operations.
```{r}
set.seed(100)

Df1 <- iris[sample(1:nrow(iris), 10), c(1,2,3,5)]

Df2 <- iris[sample(1:nrow(iris), 10), c(1,2,4,5) ]

# induce NAs

Df1 <- Df1[sample(1:nrow(Df1), 3), 4]

Df2 <- Df2[sample(1:nrow(Df1), 3), 4]
```






Q16. Create customised character vector using the paste function

Exercise 16: Create this character vector using paste: 'var1', 'var2', 'var3', 'pred1', 'pred2', 'pred3'
```{r}
paste0 (c(rep("var", 3), rep("pred", 3)), 1:3)
```






Q17. Creating tables

Exercise 17: Tabulate the Sepal.Width for each Species from iris
```{r}
table(iris$Species, iris$Sepal.Width)
```






Q18. Create a logic for the above problem using a For-loop

Exercise 18: Make the logic for above problem statement using a 'for-loop' and a 'if-else' statement
```{r}
output <- character(nrow(iris))

for(i in c(1:nrow(iris))){

if (iris$Sepal.Length[i] > 5){

output[i] <- "greater than 5"

} else {

output[i] <- "lesser than 5"

}

}
```







Q19. ifelse() function

Exercise 19: Make the logic for above problem statement using a ifelse() function
```{r}
output <- ifelse(iris$Sepal.Length > 5, "greater than 5", "lesser than 5") # works like the 'if' function in MS Excel, except that the condition is checked for every element of iris$Sepal.Length

output
```







Q20. The apply() function


Exercise 20: Create a logic for the same problem statement using apply() function
```{r}
# define the function for apply() statement

myFunc <- function(x){

if(x['Sepal.Length'] > 5){

"greater than 5"

} else {

"lesser than 5"

}

}

output <- apply(iris, 1, FUN=myFunc)

output
```

